---
title: "Diagnostic for residual tumor after TACE: Contrast enhanced ultrasound vs volume perfusion
computed tomography"
author: "Made Vidyasti Laksita Wijaya, Kadek Adit Wiryadana"
date: "Buleleng, `r Sys.Date()`"
output: html_document
reference: ref.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

TACE is currently the treatment of choice for intermediate stage HCCs [4,208].
The rationale of TACE treatment rests in the super-selective delivery of embolization
particles (lipiodol or drug-eluting beads) together with a chemotherapeutic drug (usually
Epirubicin), thereby aiming to induce complete anoxia of the malignant tissue area. This
causes selective necrosis of the tumor lesion, sparing as much normal liver parenchyma
as possible [216]. Even though TACE might achieve a complete therapeutic response, it
is still considered a palliative method, since small numbers of malignant cells can escape
necrosis. Early detection of such areas will warrant a chance for repeat treatment, usually
with a second TACE session [217].

## Methods

### PIRO
### Literature Search
### Eligibility Criteria
### Data Collection
### Risk of Bias and Quality Assement
### Statistical Analysis

## Results

```{r library}
library(tidyverse)
library(googlesheets4)
library(mada)
```

```{r load_data}
ceus <- read_sheet("https://docs.google.com/spreadsheets/d/1LhmtJKSN0qNRz2zOt-TA7zN7KZl85KZ9n_kQDyosius/edit#gid=0", sheet = 1)

vpct <- read_sheet("https://docs.google.com/spreadsheets/d/1LhmtJKSN0qNRz2zOt-TA7zN7KZl85KZ9n_kQDyosius/edit#gid=1605849085", sheet = 2)

```

### Search Results

### Findings

```{r descriptive analysis}

```


## Discussion

### Summary of the Results
### Limitations
### Applications

## Conclusion

## Disclaimer

## References

## Abstract