---
title: "Utility contrast enhanced ultrasonography for detecting residual liver tumor early after transarterial chemoembolization: A diagnostic metanalysis"
author: "Made Vidyasti Laksita Wijaya, Kadek Adit Wiryadana"
date: "Buleleng, `r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
bibliography: ref.bib
csl: nature-publishing-group-vancouver.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F)
```

## Introduction

Transarterial chemoembolization (TACE) is the recommended treatment of choice for intermediate stage HCCs.[@Kudo_2019] The underlying principle of TACE is inducing tumor tissue hypoxia with the selective delivery of embolization particles together with a chemotherapeutic drug. TACE is still considered a palliative method, although it might achieve a complete therapeutic response, small numbers of malignant cells can escape necrosis.[@Liapi_2010] Early evaluation and detection of those residual tumor warrant a chance for immediate repeat treatment.[@wobser_2014; @shiozawa_2021; @takizawa_2013; @watanabe_2020] Thereby, the modality for early detection is paramount important. The most promising modality is the contrast-enhanced ultrasonography (CEUS). This study aimed to gather evidence for diagnostic performance of CEUS in detecting residual tumor within 24-72 hours after TACE treatment.

## Methods
### Literature Search
### Study Selection
### Data Collection
### Risk of Bias and Quality Assement
### Statistical Analysis

## Results

```{r library, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(googlesheets4)
library(mada)
```

```{r load_data, eval=FALSE}
ceus <- read_sheet("https://docs.google.com/spreadsheets/d/1KOU8NsU6CDHBgILqSRq5UJEILpI68aSKXwZbCBfQPkc/edit#gid=1923082983", sheet = 1)
 
write_csv(ceus, "ceus.csv")
```

```{r read_data, include=FALSE}
ceus <- read_csv("ceus.csv")
#ceus <- ceus[1:3,]
```


### Search Results

### Findings

```{r descriptive analysis}
des_ceus <- madad(ceus,
                  TP=TP,
                  FN=FN,
                  FP=FP,
                  TN=TN)
print(des_ceus)
```

```{r forest_plot_sensitivity}
forest_sens <- mada::forest(des_ceus, 
               type = "sens",
               snames = ceus$Author,
               main= "Sensitivity")

```

```{r forest_plot_specificity}
forest_spec <- mada::forest(des_ceus,
               type = "spec",
               snames = ceus$Author,
               main = "Specificity")
```

```{r crosshair_plot}
crosshair(ceus, 
          col= factor(ceus$Author))
```

```{r roc-ecllipse}
ROCellipse(ceus)
```

```{r reitsma}
fit1 <- reitsma(ceus)
summary(fit1)

plot(fit1, predict=TRUE)
```


## Discussion

### Summary of the Results
### Limitations
### Applications

## Conclusion

## Disclaimer

## References

<div id="refs"></div>


## Abstract