---
title: "Contrast enhanced ultrasonography for early diagnostic of residual liver tumor after transarterial chemoembolization: A diagnostic metanalysis"
author: "Made Vidyasti Laksita Wijaya, Kadek Adit Wiryadana"
date: "Buleleng, `r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
reference: ref.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F)
```

## Introduction

TACE is currently the treatment of choice for intermediate stage HCCs [4,208]. The rationale of TACE treatment rests in the super-selective delivery of embolization particles (lipiodol or drug-eluting beads) together with a chemotherapeutic drug (usually Epirubicin), thereby aiming to induce complete anoxia of the malignant tissue area. This causes selective necrosis of the tumor lesion, sparing as much normal liver parenchyma as possible [216]. Even though TACE might achieve a complete therapeutic response, it is still considered a palliative method, since small numbers of malignant cells can escape necrosis. Early detection of such areas will warrant a chance for repeat treatment, usually with a second TACE session [217].

## Methods

### PIRO
### Literature Search
### Eligibility Criteria
### Data Collection
### Risk of Bias and Quality Assement
### Statistical Analysis

## Results

```{r library, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(googlesheets4)
library(mada)
```

```{r load_data, eval=FALSE}
ceus <- read_sheet("https://docs.google.com/spreadsheets/d/1KOU8NsU6CDHBgILqSRq5UJEILpI68aSKXwZbCBfQPkc/edit#gid=1923082983", sheet = 1)
 
write_csv(ceus, "ceus.csv")
```

```{r read_data, include=FALSE}
ceus <- read_csv("ceus.csv")
```


### Search Results

### Findings

```{r descriptive analysis}
des_ceus <- madad(ceus,
                  TP=TP,
                  FN=FN,
                  FP=FP,
                  TN=TN)
print(des_ceus)
```

```{r forest_plot_sensitivity}
forest_sens <- mada::forest(des_ceus, 
               type = "sens",
               snames = ceus$Author,
               main= "Sensitivity")

```

```{r forest_plot_specificity}
forest_spec <- mada::forest(des_ceus,
               type = "spec",
               snames = ceus$Author,
               main = "Specificity")
```

```{r crosshair_plot}
crosshair(ceus, 
          col= factor(ceus$Author))
```

```{r roc-ecllipse}
ROCellipse(ceus)
```

```{r reitsma}
fit1 <- reitsma(ceus)
summary(fit1)

plot(fit1, predict=TRUE)
```


## Discussion

### Summary of the Results
### Limitations
### Applications

## Conclusion

## Disclaimer

## References

## Abstract